---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# everydaysizes

<!-- badges: start -->
<!-- badges: end -->

The goal of {everydaysizes} is to give you a set of every day items with their 
dimensions. 

## Installation

You can not yet install the released version of everydaysizes from [CRAN](https://CRAN.R-project.org) with:

``` r
#install.packages("everydaysizes")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("RMHogervorst/everydaysizes")
```
## Example

This is a basic example which shows you what is in the package.
The Package at this moment contains 2 datasets with objects and their dimensions
in units. 

```{r example}
library(everydaysizes)
library(units)
tail(everyday_items, 4)
```

```{r}
library(tidyverse)
library(ggforce)
(devices <- 
  everyday_items %>% 
  filter(type == "device") )
```

```{r}
ggplot(devices, aes(height, width, label = what)) +
  geom_text()
ggplot(devices, aes(height, depth, label = what)) +
  geom_text()
```
